Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm.tex
edits to shorten section 4, down to 14 pages

\section{Main Algorithm and Analysis}
\label{sec:ub}
The algorithm achieving the claimed bounds of
Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

@@

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than
$1/\log(s)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s)$.
\end{itemize}

@@

Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
arms; thus, by pulling some other arm $i'$, an arm $i$ may become
payment-eligible, or cease to be so.
Algorithm~\ref{alg:basic-incentivizing} gives the full details.

>>>>

\section{Main Algorithm and Analysis}
\label{sec:ub}
The algorithm achieving the claimed bounds of
Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled
it incentivizes this arm with a payment high enough
to guarantee the next agent pulls it.
This way the algorithm ensures each arm is pulled often enough.

@@

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item 
The conditional probability of pulling arm $i$ is less than
$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
attribute vectors.  In other words, we require
$\PullProb{t}{i} < 1/\log(s)$ where 
$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
is the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
\end{itemize}

@@

Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
arms; thus, by pulling another arm $i'$, an arm $i$ may become
payment-eligible, or cease to be so.
Algorithm~\ref{alg:basic-incentivizing} gives the full details.
